---
title: "Visualization"
output: github_document
---

```{r}
library(tidyverse)
library(ggridges)

library(p8105.datasets)
data("weather_df")
```

Now we have everything we need.

```{r}
weather_df
```


scatter plot

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax))
```

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point()
```

```{r}
ggp_temp_scatterplot =
  weather_df |>
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()

ggp_temp_scatterplot
```

color label(colour = ), transparent (alpha = ), smooth curve(geom_smooth = )

```{r}
weather_df |>
  ggplot(aes(x = tmin, y = tmax, colour = name)) + 
  geom_point(alpha = 0.25)+
  geom_smooth(se = FALSE)
```

#把`colour/color`放到`ggplot(aes())`：**点和拟合线都会按 name 分组，多条线**
#把`colour/color`放到`geom_point(aes())`：**只有点分组上色，平滑曲线用全部数据画一条**

```{r}
weather_df |>
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name),alpha = 0.25)+
  geom_smooth(se = FALSE)
```


Show faceting(separate by ...)

```{r}
weather_df |>
  ggplot(aes(x = tmin, y = tmax, colour = name)) + 
  geom_point(alpha = 0.5)+
  facet_grid(. ~ name)
```

```{r}
weather_df |>
  ggplot(aes(x = tmin, y = tmax, colour = name)) + 
  geom_point(alpha = 0.5)+
  facet_grid(name ~ .)
```

```{r}
weather_df |>
  ggplot(aes(x = tmin, y = tmax, colour = name)) + 
  geom_point(alpha = 0.5)+
  facet_grid(cols = vars(name))
```


let's look at something else.

```{r}
weather_df |>
  ggplot(aes(x = date, y = tmax, colour = name)) + 
  geom_point(aes(size = prcp),alpha = 0.5) +
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```


```{r}
weather_df |>
  filter(name == "CentralPark_NY") |>
  mutate(
    tmax = tmax * (9 / 5) + 32,
    tmax = tmax * (9 / 5) + 32

  ) |>
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```
`mutate()`：**新增列，或者原地修改现有列**，返回完整的数据集（保留原来所有列）

what's a hexplot

```{r}

weather_df |>
  ggplot(aes(x = tmin, y = tmax)) +
  geom_hex()
```

## univariate plots

```{r}
weather_df |>
  ggplot(aes(x = tmax)) +
  geom_histogram()
```

```{r}
weather_df |>
  ggplot(aes(x = tmax, fill = name)) +
  geom_histogram(pos = "dodge")
```

```{r}
weather_df |>
  ggplot(aes(x = tmax, fill = name)) +
  geom_histogram() + 
  facet_grid(. ~ name)
```

Density plots

```{r}
weather_df |>
  ggplot(aes(x = tmax, colour = name)) +
  geom_density()
```

fill 填色

```{r}
weather_df |>
  ggplot(aes(x = tmax, fill = name)) +
  geom_density(alpha = 0.3)
```


boxplot

```{r}
weather_df |>
  ggplot(aes(y = tmax)) +
  geom_boxplot()
```

加x会根据x生成多个


```{r}
weather_df |>
  ggplot(aes(x = name, y = tmax)) +
  geom_boxplot()
```

Violin

```{r}
weather_df |>
  ggplot(aes(x = name, y = tmax)) +
  geom_violin()
```

ridge plots

```{r}
weather_df |>
  ggplot(aes(x = tmax, y = name)) +
  geom_density_ridges()
```

